\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-07-15 paper.qmd
Update the hexbinning text

To make the grid, a buffer parameter ($q$) is set as a proportion of the plot space. By default this is 0.1. A value should be chosen to provide at buffer of a full hexagon width ($a_1$) and height ($a_2$) for the grid to extend beyond the data, in all directions. The lower left position where the grid starts is defined as $(s_1, s_2)$, and corresponds to the centroid of the lowest left hexagon. This must be smaller than the minimum data value. This is computed as one buffer unit, $q$ below the minimum data value, by default. The user provides the preferred number of bins in the horizontal direction, $b_1$, and the algorithm computes the appropriate number of bins in the vertical direction, $b_2$.

The value for $b_2$ is computed by fixing $b_1$. Considering the lower bound of the NLDR, $a_1 > -2q$, and $a_1 > \frac{1+q}{b_1 -1}$. Similarly, according to the upper bound of the NLDR, $a_1 > \frac{2r_2(1 + q)}{\sqrt{3}(b_2 - 1)}$, because $a_2 = \frac{\sqrt(3)}{2}a_1$ for regular hexagons. Therefore, $b_2 = \Big\lceil1 +\frac{2r_2(b_1 - 1)}{\sqrt{3}}\Big\rceil$.

>>>>

To make the grid, a buffer parameter ($q$) is set as a proportion of the plot space. By default this is 0.1. A value should be chosen to provide at buffer of a full hexagon width ($a_1$) and height ($a_2$) for the grid to extend beyond the data, in all directions. The lower left position where the grid starts is defined as $(s_1, s_2)$, and corresponds to the centroid of the lowest left hexagon. This must be smaller than the minimum data value.
This is computed as $s_1 = -q - a_1$, and $s_2 = -q \times r_2$ to have buffer around the data space. <!-- This is computed as one buffer unit, $q$ below the minimum data value, by default.--> The user provides the preferred number of bins in the horizontal direction, $b_1$, and the algorithm computes the appropriate number of bins in the vertical direction, $b_2$.

The value for $b_2$ is computed by fixing $b_1$. Considering the upper bound of the first NLDR component, $a_1 > \frac{1+q}{b_1 -3}$. Similarly, for the second NLDR component, $a_2 > \frac{r_2(1 + q)}{(b_2 - 2)}$. Since $a_2 = \frac{\sqrt(3)}{2}a_1$ for regular hexagons, $a_1 > \frac{2r_2(1 + q)}{\sqrt{3}(b_2 - 2)}$. This is a linear optimization problem. Therefore, the optimal solution must occur on a vertex. Therefore, $b_2 = \Big\lceil2 +\frac{2r_2(b_1 - 3)}{\sqrt{3}}\Big\rceil$.

### 2024-07-15 paper.tex
Update with quollr 1.4 version
Update the hexbinning text

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-1in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{1.7in}%
\addtolength{\topmargin}{-1in}%
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{float}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage{bm}
\def\tightlist{}
\usepackage{setspace}
\newcommand\pD{$p\text{-}D$}
\newcommand\kD{$k\text{-}D$}
\newcommand\dD{$d\text{-}D$}
\newcommand\gD{$2\text{-}D$}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{agsm}
\usepackage{bookmark}

@@

To make the grid, a buffer parameter (\(q\)) is set as a proportion of
the plot space. By default this is 0.1. A value should be chosen to
provide at buffer of a full hexagon width (\(a_1\)) and height (\(a_2\))
for the grid to extend beyond the data, in all directions. The lower
left position where the grid starts is defined as \((s_1, s_2)\), and
corresponds to the centroid of the lowest left hexagon. This must be
smaller than the minimum data value. This is computed as one buffer
unit, \(q\) below the minimum data value, by default. The user provides
the preferred number of bins in the horizontal direction, \(b_1\), and
the algorithm computes the appropriate number of bins in the vertical
direction, \(b_2\).

The value for \(b_2\) is computed by fixing \(b_1\). Considering the
lower bound of the NLDR, \(a_1 > -2q\), and
\(a_1 > \frac{1+q}{b_1 -1}\). Similarly, according to the upper bound of
the NLDR, \(a_1 > \frac{2r_2(1 + q)}{\sqrt{3}(b_2 - 1)}\), because
\(a_2 = \frac{\sqrt(3)}{2}a_1\) for regular hexagons. Therefore,
\(b_2 = \Big\lceil1 +\frac{2r_2(b_1 - 1)}{\sqrt{3}}\Big\rceil\).

@@

\captionsetup{labelsep=none}\includegraphics{figures/mnist/sc_1.png}

@@

\captionsetup{labelsep=none}\includegraphics{figures/mnist/sc_2.png}

@@

\captionsetup{labelsep=none}\includegraphics{figures/mnist/sc_3.png}

>>>>

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother

@@

\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-1in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{1.7in}%
\addtolength{\topmargin}{-1in}%
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{float}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage{bm}
\def\tightlist{}
\usepackage{setspace}
\newcommand\pD{$p\text{-}D$}
\newcommand\kD{$k\text{-}D$}
\newcommand\dD{$d\text{-}D$}
\newcommand\gD{$2\text{-}D$}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{agsm}
\usepackage{bookmark}

@@

To make the grid, a buffer parameter (\(q\)) is set as a proportion of
the plot space. By default this is 0.1. A value should be chosen to
provide at buffer of a full hexagon width (\(a_1\)) and height (\(a_2\))
for the grid to extend beyond the data, in all directions. The lower
left position where the grid starts is defined as \((s_1, s_2)\), and
corresponds to the centroid of the lowest left hexagon. This must be
smaller than the minimum data value. This is computed as
\(s_1 = -q - a_1\), and \(s_2 = -q \times r_2\) to have buffer around
the data space. The user provides the preferred number of bins in the
horizontal direction, \(b_1\), and the algorithm computes the
appropriate number of bins in the vertical direction, \(b_2\).

The value for \(b_2\) is computed by fixing \(b_1\). Considering the
upper bound of the first NLDR component, \(a_1 > \frac{1+q}{b_1 -3}\).
Similarly, for the second NLDR component,
\(a_2 > \frac{r_2(1 + q)}{(b_2 - 2)}\). Since
\(a_2 = \frac{\sqrt(3)}{2}a_1\) for regular hexagons,
\(a_1 > \frac{2r_2(1 + q)}{\sqrt{3}(b_2 - 2)}\). This is a linear
optimization problem. Therefore, the optimal solution must occur on a
vertex. Therefore,
\(b_2 = \Big\lceil2 +\frac{2r_2(b_1 - 3)}{\sqrt{3}}\Big\rceil\).

@@

\includegraphics{figures/mnist/sc_1.png}

@@

\includegraphics{figures/mnist/sc_2.png}

@@

\includegraphics{figures/mnist/sc_3.png}
